### 2018-11-09 Sections/quantum_repeater_networks.tex
braket
Finished braket

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{repeaters_1}
\captionspacefig \caption{(a) Schematic representation of an entangled Bell pair $| \Psi\rangle_{A,B}$ shared between remote parties Alice and Bob. The two solid dots represent physical qubits, while the edge represents entanglement. (b) The link may be over a long distance $L_{\rm tot}$. (c) Due to channel losses the link may be broken into $N$ smaller segments of length $L$. The links for each of the smaller segments can be independently generated and combined to form the longer distance link.} 
\label{fig:repeaters_1}
\end{figure}

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
|\Psi\rangle=\frac{1}{\sqrt{2}} (|g\rangle |H\rangle + |e\rangle |V\rangle),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{repeaters_3}
\captionspacefig \caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitters}\index{Polarising beamsplitters} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
|\Psi\rangle &= \frac{1}{2} |g\rangle |g\rangle |H\rangle |H\rangle +\frac{1}{2} |e\rangle |e\rangle |V\rangle |V\rangle \nonumber \\
&+\frac{1}{2} |g\rangle |e\rangle |HV\rangle |0\rangle + \frac{1}{2} |e\rangle |g\rangle |0\rangle |HV\rangle. 
\end{align}

One immediately notices that the $|g\rangle |e\rangle$ and $|e\rangle |g\rangle$ contributions are associated with two photons in one of the PBS exit modes, the other being in the vacuum state. However, the $|g\rangle |g\rangle$ and $|e\rangle |e\rangle$ terms have one photon in each of the output modes. They are of opposite polarisation, but measuring those photons in the diagonal/anti-diagonal ($\hat{X}$) basis erases this `which-path' information\index{Which-path erasure} yielding an equal superposition of the two alternative histories -- an entangled Bell state\index{Bell states} of the form,
\begin{align}
|\Psi_\pm\rangle=\frac{1}{\sqrt{2}} (|g\rangle |g\rangle \pm |e\rangle |e\rangle),
\end{align}
where the sign is given by the parity of the two photo-detection outcomes in the $\hat{X}$ basis. This entangled state is stored in the quantum memories between nodes.

@@

In any entanglement distribution scheme for quantum networks, the repeater nodes are spatially separated and one must consider channel losses, which are the dominant error source. Channel loss in this situation implies that we do not register a coincidence event between $D_1$ and $D_2$, which heralds the entanglement. Thus our entanglement distribution success probability is reduced. In fact, the heralded probability of success can be expressed as,
\begin{align}
p_\mathrm{ED}= \frac{1}{2} e^{-L/L_0} {p_\mathrm{det}}^2,
\end{align} 
where $L$ is the distance between the two repeater nodes with $L_0$ being the attenuation length of the channel, while $p_\mathrm{det}$ is the detector efficiency. Here we have ignored the source and coupling efficiencies. It is immediately obvious from this expression that the further the repeater nodes are apart, the lower the probability of success, on an exponentially decaying trajectory. The attenuation length of typical telecom optical fibre is approximately 22.5km and so the average time to generate a distributed entangled pair is,
\begin{align}
T_\mathrm{av} &\sim \frac{L}{ c \cdot p_\mathrm{ED}}\nonumber\\
&= \frac{2 L e^{L/L_0}}{ c \cdot {p_\mathrm{det}}^2}
\end{align} 
where $c$ is the speed of light in the channel. This grows exponentially against node separation and so places important constraints on the lifetime of the quantum memories. If we consider pure dephasing effects on our matter qubits, the state of our system can be represented by,
\begin{align}
\hat\rho(F) = F |\Psi^+\rangle \langle \Psi^+|+(1-F) |\Psi^-\rangle \langle \Psi^-|,
\label{eq:rho_bell_fid}
\end{align} 
where $F$ is the fidelity of our entangled state given by,
\begin{align}
F=\frac{1+e^{-t/\tau_\mathrm{D}}}{2},
\end{align} 
with $t$ being the duration over which the entangled state is held in memory, while $\tau_\mathrm{D}$ is the coherence time of the memory. If one only requires a single Bell pair and no further operation are performed, then \mbox{$t=c/L$}. However in a more general setting where multiple pairs are required, the time will be $T_\mathrm{av}$ on average, which is inversely proportional to the probability of generating the entangled state. The quality of the prepared remote entangled state may therefore not be sufficient for the tasks it is required for due to these finite memory lifetimes or operational gate errors. One needs to be able to purify these entangled resources.

@@

In this simplest purification protocol, Alice and Bob share two pairs of entangled states of the form given by Eq.~(\ref{eq:rho_bell_fid}). These states are a mixture of only two Bell states. We begin our purification protocol by using local operations to transform $\hat\rho$ to,
\begin{align}\label{eq:rho_bell_fid_dash}
\hat\rho(F)=F |\Psi^+\rangle \langle \Psi^+|+(1-F) |\Phi^+\rangle \langle \Phi^+|,
\end{align}

@@

The probability of obtaining the even parity outcome is,
\begin{align}
	p_\mathrm{even}=\frac{F^2+(1-F)^2}{2}.
\end{align}
Alternatively for the odd parity measurement results, which occur with probability,
\begin{align}
	p_\mathrm{odd}=F(1-F),
\end{align}
the resulting state is an equal mixture of $|\Psi^+\rangle$ and $|\Phi^+\rangle$ and is not entangled at all. In this case we must start again from scratch with the entanglement distribution.

@@

Consider a four photon state of the form,
\begin{align}
|\Psi\rangle &= \alpha \left(|0\rangle_1 |0\rangle_2+|1\rangle_1 |1\rangle_2\right) \otimes \left(|0\rangle_3 |0\rangle_4+|1\rangle_3 |1\rangle_4\right) \nonumber \\
&+ \beta \left(|0\rangle_1 |1\rangle_2+|1\rangle_1 |0\rangle_2\right) \otimes \left(|0\rangle_3 |1\rangle_4+|1\rangle_3 |0\rangle_4\right),
\end{align}
where $|0\rangle$ and $|1\rangle$ represent orthogonal degrees of freedom (e.g polarisation). This state can be rewritten in the form,
\begin{align}\label{eq:third_gen_red_enc}
|\Psi\rangle = \alpha |\Phi_{12}^+\rangle  |\Phi_{34}^+\rangle+\beta |\Psi_{12}^+\rangle  |\Psi_{34}^+\rangle,
\end{align}
and thus the state has been encoded into terms of a tensor product of two redundantly encoded Bell states. Now photon loss will remove one of these photons. As an example, let us consider what happens when photon 4 is lost. The resultant state can be represented by the density matrix,
\begin{align}
	\hat\rho= |\zeta^+\rangle \langle \zeta^+| +|\zeta^-\rangle \langle \zeta^-|,
	\end{align}
where,
\begin{align}
|\zeta^+\rangle &=  \alpha |\Phi_{12}^+\rangle |0\rangle_3 + \beta  |\Psi_{12}^+\rangle |1\rangle_3, \nonumber \\
|\zeta^-\rangle &=  \alpha |\Phi_{12}^+\rangle |1\rangle_3 + \beta  |\Psi_{12}^+\rangle |0\rangle_3.
\end{align}

We immediately notice that \mbox{$|\zeta^-\rangle=\hat{X}_3 |\zeta^+\rangle$} and so by measuring the third photon in the $\hat{X}$ basis our state reduces to the pure state \mbox{$\alpha |\Phi_{12}^+\rangle \pm \beta |\Psi_{12}^+\rangle$}, where the $\pm$ sign is given by the $\hat{X}$ measurement outcome. This is then correctable using local operations. After the loss event of photon 4 and the measurement of the third photon our state thus becomes,
\begin{align}
\alpha |\Phi_{12}^+\rangle + \beta  |\Psi_{12}^+\rangle,
\end{align}
which has exactly the same information in it as $|\Psi\rangle$ but without the redundant encoding.

@@

The above example illustrates how the smallest optical loss code work. The general code with \mbox{$n - 1$} redundancy can be written as \cite{bib:ralph05, bib:munro12},
\begin{align}
|\Psi\rangle = \alpha |\Phi_{e}\rangle_1 \ldots  |\Phi_{{e}}\rangle_n+\beta |\Psi_{o}\rangle_1 \ldots  |\Psi_{o}\rangle_n
\end{align}
where $|\Phi_{e,o}\rangle$ are the even and odd parity m photon states given by,
\begin{align}
|\Phi_{e,o}\rangle = \frac{1}{\sqrt{2}}(|+\rangle_1 \ldots  |+\rangle_m\pm |-\rangle_1 \ldots  |-\rangle_m),
\end{align}
with \mbox{$|\pm\rangle=\frac{1}{\sqrt{2}}(|0\rangle\pm |1\rangle)$}. This redundancy-based parity code is composed of $n$ logical qubits each containing $m$ photons. For this code to correct loss errors we have two constraints,
\begin{itemize}
\item At least one logical qubit must arrive without photon loss.
\item Every logical qubit must have at least one photon arrive successfully.
\end{itemize}
If these constraints are met, the loss events during transmission between adjacent repeater nodes can be corrected. Of course, such codes can not correct more than fifty percent errors and so the distance between repeater nodes is limited. Remembering that the probability of a photon being successfully transmitted through a channel of length $L$ with attenuation length $L_0$ is given by \mbox{$p=e^{-L/L_0}$}, the maximum distance between repeater nodes is \mbox{$L/L_0\sim 0.69$} (which corresponds to approximately 17km in present-day commercial telecom fibre). This is much shorter than what we would typically consider for the first and second-generation schemes.

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{repeaters_1}
\captionspacefig \caption{(a) Schematic representation of an entangled Bell pair $\ket{\Psi}_{A,B}$ shared between remote parties Alice and Bob. The two solid dots represent physical qubits, while the edge represents entanglement. (b) The link may be over a long distance $L_{\rm tot}$. (c) Due to channel losses the link may be broken into $N$ smaller segments of length $L$. The links for each of the smaller segments can be independently generated and combined to form the longer distance link.} 
\label{fig:repeaters_1}
\end{figure}

@@

Ideally one wants to initially generate a maximally entangled state of the form \cite{bib:WJM2015},
\begin{align}
\ket{\Psi}=\frac{1}{\sqrt{2}} (\ket{g}\bra{H} + \ket{e}\bra{V}),
\end{align}
within the repeater node, where $\ket{g}$ and $\ket{e}$ are the two states (ground and excited) of the quantum memory, and $\ket{H}$ and $\ket{V}$ are the polarisation states of a single photon. 
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{repeaters_3}
\captionspacefig \caption{Entanglement distribution scheme based on quantum emitters and which-path erasure\index{Which-path erasure}. Each node emits a photon entangled with the quantum memories present within that nodes. The photons from the adjacent repeater nodes then interfere on a beamsplitter (or polarising beamsplitter)\index{Beamsplitters}\index{Polarising beamsplitters} which erases information about which path the photon took. The photons are then measured in an appropriate basis to project the quantum memories within the nodes onto an entangled state.} 
\label{fig:repeaters_3}
\end{figure} 
The photons from the two repeater nodes (Fig.~\ref{fig:repeaters_3}) are then transmitted to a beamsplitter (or PBS in this example), after which the state of the system is,
\begin{align}
\ket{\Psi} &= \frac{1}{2} \ket{g} \ket{g} \ket{H} \ket{H} +\frac{1}{2} \ket{e} \ket{e} \ket{V} \ket{V} \nonumber \\
&+\frac{1}{2} \ket{g} \ket{e} |\ket{HV} \ket{0} + \frac{1}{2} \ket{e} \ket{g} \ket{0}\ket{HV}. 
\end{align}

One immediately notices that the $\ket{g} \ket{e}$ and $\ket{e}\ket{g}$ contributions are associated with two photons in one of the PBS exit modes, the other being in the vacuum state. However, the $\ket{g}\ket{g}$ and $\ket{e}\ket{e}$ terms have one photon in each of the output modes. They are of opposite polarisation, but measuring those photons in the diagonal/anti-diagonal ($\hat{X}$) basis erases this `which-path' information\index{Which-path erasure} yielding an equal superposition of the two alternative histories -- an entangled Bell state\index{Bell states} of the form,
\begin{align}
\ket{\Psi_\pm}=\frac{1}{\sqrt{2}} (\ket{g}\ket{g} \pm \ket{e}\ket{e}),
\end{align}
where the sign is given by the parity of the two photo-detection outcomes in the $\hat{X}$ basis. This entangled state is stored in the quantum memories between nodes.

@@

In any entanglement distribution scheme for quantum networks, the repeater nodes are spatially separated and one must consider channel losses, which are the dominant error source. Channel loss in this situation implies that we do not register a coincidence event between $D_1$ and $D_2$, which heralds the entanglement. Thus our entanglement distribution success probability is reduced. In fact, the heralded probability of success can be expressed as,
\begin{align}
p_\mathrm{ED}= \frac{1}{2} e^{-L/L_0} {p_\mathrm{det}}^2,
\end{align} 
where $L$ is the distance between the two repeater nodes with $L_0$ being the attenuation length of the channel, while $p_\mathrm{det}$ is the detector efficiency. Here we have ignored the source and coupling efficiencies. It is immediately obvious from this expression that the further the repeater nodes are apart, the lower the probability of success, on an exponentially decaying trajectory. The attenuation length of typical telecom optical fibre is approximately 22.5km and so the average time to generate a distributed entangled pair is,
\begin{align}
T_\mathrm{av} &\sim \frac{L}{ c \cdot p_\mathrm{ED}}\nonumber\\
&= \frac{2 L e^{L/L_0}}{ c \cdot {p_\mathrm{det}}^2}
\end{align} 
where $c$ is the speed of light in the channel. This grows exponentially against node separation and so places important constraints on the lifetime of the quantum memories. If we consider pure dephasing effects on our matter qubits, the state of our system can be represented by,
\begin{align}
\hat\rho(F) = F \ket{\Psi^+} \bra{\Psi^+}+(1-F) \ket{\Psi^-}\bra{\Psi^-},
\label{eq:rho_bell_fid}
\end{align} 
where $F$ is the fidelity of our entangled state given by,
\begin{align}
F=\frac{1+e^{-t/\tau_\mathrm{D}}}{2},
\end{align} 
with $t$ being the duration over which the entangled state is held in memory, while $\tau_\mathrm{D}$ is the coherence time of the memory. If one only requires a single Bell pair and no further operation are performed, then \mbox{$t=c/L$}. However in a more general setting where multiple pairs are required, the time will be $T_\mathrm{av}$ on average, which is inversely proportional to the probability of generating the entangled state. The quality of the prepared remote entangled state may therefore not be sufficient for the tasks it is required for due to these finite memory lifetimes or operational gate errors. One needs to be able to purify these entangled resources.

@@

In this simplest purification protocol, Alice and Bob share two pairs of entangled states of the form given by Eq.~(\ref{eq:rho_bell_fid}). These states are a mixture of only two Bell states. We begin our purification protocol by using local operations to transform $\hat\rho$ to,
\begin{align}\label{eq:rho_bell_fid_dash}
\hat\rho(F)=F \ket{\Psi^+}\bra{\Psi^+}+(1-F) \ket{\Phi^+}\bra{\Phi^+},
\end{align}

@@

The probability of obtaining the even parity outcome is,
\begin{align}
	p_\mathrm{even}=\frac{F^2+(1-F)^2}{2}.
\end{align}
Alternatively for the odd parity measurement results, which occur with probability,
\begin{align}
	p_\mathrm{odd}=F(1-F),
\end{align}
the resulting state is an equal mixture of $\ket{\Psi^+}$ and $\ket{\Phi^+}$ and is not entangled at all. In this case we must start again from scratch with the entanglement distribution.

@@

Consider a four photon state of the form,
\begin{align}
\ket{\Psi} &= \alpha \ket{0}_1 \ket{0}_2+\ket{1}_1 \ket{1}_2) \otimes (\ket{0}_3 \ket{0}_4+\ket{1}_3 \ket{1}_4) \nonumber \\
&+ \beta (\ket{0}_1 \ket{1}_2+\ket{1}_1 \ket{0}_2) \otimes (\ket{0}_3 \ket{1}_4+\ket{1}_3 \ket{0}_4),
\end{align}
where $\ket{0}$ and $\ket{1}$ represent orthogonal degrees of freedom (e.g polarisation). This state can be rewritten in the form,
\begin{align}\label{eq:third_gen_red_enc}
\ket{\Psi} = \alpha \ket{\Phi_{12}^+} \ket{\Phi_{34}^+}+\beta \ket{\Psi_{12}^+} \ket{\Psi_{34}^+},
\end{align}
and thus the state has been encoded into terms of a tensor product of two redundantly encoded Bell states. Now photon loss will remove one of these photons. As an example, let us consider what happens when photon 4 is lost. The resultant state can be represented by the density matrix,
\begin{align}
	\hat\rho= \ket{\zeta^+} \bra{\zeta^+} +\ket{\zeta^-}\bra{\zeta^-},
	\end{align}
where,
\begin{align}
\ket{\zeta^+} &=  \alpha \ket{\Phi_{12}^+} \ket{0}_3 + \beta  \ket{\Psi_{12}^+} \ket{1}_3, \nonumber \\
\ket{\zeta^-} &=  \alpha \ket{\Phi_{12}^+} \ket{1}_3 + \beta  \ket{\Psi_{12}^+} \ket{0}_3.
\end{align}

We immediately notice that \mbox{$\ket{\zeta^-}=\hat{X}_3 \ket{\zeta^+}$} and so by measuring the third photon in the $\hat{X}$ basis our state reduces to the pure state \mbox{$\alpha \ket{\Phi_{12}^+} \pm \beta \ket{\Psi_{12}^+}$}, where the $\pm$ sign is given by the $\hat{X}$ measurement outcome. This is then correctable using local operations. After the loss event of photon 4 and the measurement of the third photon our state thus becomes,
\begin{align}
\alpha \ket{\Phi_{12}^+} + \beta  \ket{\Psi_{12}^+},
\end{align}
which has exactly the same information in it as $\ket{\Psi}$ but without the redundant encoding.

@@

The above example illustrates how the smallest optical loss code work. The general code with \mbox{$n - 1$} redundancy can be written as \cite{bib:ralph05, bib:munro12},
\begin{align}
\ket{\Psi} = \alpha \ket{\Phi_{e}}_1 \ldots  \ket{\Phi_e}_n+\beta \ket{\Psi_{o}}_1 \ldots  \ket{\Psi_{o}}_n
\end{align}
where $\ket{\Phi_{e,o}}$ are the even and odd parity m photon states given by,
\begin{align}
\ket{\Phi_{e,o}} = \frac{1}{\sqrt{2}}(\ket{+}_1 \ldots  \ket{+}_m\pm \ket{-}_1 \ldots  \ket{-}_m),
\end{align}
with \mbox{$\ket{\pm}=\frac{1}{\sqrt{2}}(\ket{0}\pm \ket{1})$}. This redundancy-based parity code is composed of $n$ logical qubits each containing $m$ photons. For this code to correct loss errors we have two constraints,
\begin{itemize}
\item At least one logical qubit must arrive without photon loss.
\item Every logical qubit must have at least one photon arrive successfully.
\end{itemize}
If these constraints are met, the loss events during transmission between adjacent repeater nodes can be corrected. Of course, such codes can not correct more than fifty percent errors and so the distance between repeater nodes is limited. Remembering that the probability of a photon being successfully transmitted through a channel of length $L$ with attenuation length $L_0$ is given by \mbox{$p=e^{-L/L_0}$}, the maximum distance between repeater nodes is \mbox{$L/L_0\sim 0.69$} (which corresponds to approximately 17km in present-day commercial telecom fibre). This is much shorter than what we would typically consider for the first and second-generation schemes.
